Figures for Paper

### 2021-09-17 paper_figures.Rmd

```{r warning=FALSE, message=FALSE}
df <- read_csv(paste0(here(),
                      "/data/itc/itc final values.csv")) %>%
    group_by(RNA) %>%
    mutate(sd =sd(kd)) %>%
    mutate(mean_kd = mean(kd))

ggplot(df, aes(x = RNA, y = kd)) +
    geom_bar(aes(x = RNA, y = mean_kd), stat="identity", position="dodge") +
    geom_point() +
    geom_errorbar(aes(x=RNA, ymin = mean_kd-sd, ymax = mean_kd+sd),
                  width = 0.3) +
    ylim(0, NA) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("")

t.test(df$kd[which(df$RNA=="H")], df$kd[which(df$RNA=="R")])
```

>>>>

```{r warning=FALSE, message=FALSE}
df <- read_csv(paste0(here(),
                      "/data/itc/itc final values.csv"))

df2 <- df %>%
    group_by(RNA, experiment) %>%
    mutate(sd2 =ifelse(is.na(sd), sd(kd), sd)) %>%
    mutate(mean_kd = mean(kd)) %>%
  ungroup() %>%
  select(experiment, RNA, mean_kd, sd2) %>%
  unique()

ggplot(df2, aes(x = experiment, fill = RNA, y = mean_kd)) +
    geom_bar(stat="identity", position="dodge") +
    #geom_point(aes(group=RNA), position="dodge") +
    geom_errorbar(aes(x=experiment, ymin = mean_kd-sd2, ymax = mean_kd+sd2,
                      fill = RNA), position="dodge") +
    ylim(0, NA) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("")

t.test(df$kd[which(df$RNA=="H" & df$experiment=="exon")], df$kd[which(df$RNA=="R" & df$experiment=="exon")])
t.test(df$kd[which(df$RNA=="H" & df$experiment=="intron")], df$kd[which(df$RNA=="R" & df$experiment=="intron")])  # this is an overestimate of significance - however still borderline significant (~0.05) when fitting error is taken into account
```
